Large-Scale Marine Protected Areas in the World's Largest Tuna Fishery

### 2019-02-05 docs/PIPA_Palau.tex
Updated all images and tables

\begin{figure}
\centering
	\includegraphics{img/VDS_year.pdf}
	\caption{\label{fig:VDS_year}Vessel-days for all PNA countries (including Tokelau).}
\end{figure}

\begin{figure}
\centering
	\includegraphics{img/VDS_country_year.pdf}
	\caption{\label{fig:VDS_country_year}Vessel-days for all PNA countries (including Tokelau) by country.
The top panel shows vessel days in absolute numbers, while the bottom panel shows the proportion
of each year. The left and right columns show fishing and non-fishing hours.}
\end{figure}

>>>>

\begin{figure}
\centering
	\includegraphics{img/all_PS_VDS_cty_year.pdf}
	\caption{\label{fig:VDS_year}a)Vessel-days for all PNA countries (including Tokelau).
	B) Vessel-days for all PNA countries (including Tokelau) by country.}
\end{figure}
